\papertitle

### 2012-10-13 manuscript.tex
Finish system concept/pose estimation

%----------------------------------------------------------------------------%
% PACKAGES
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{amsmath}

\newlength\eqnindent
\newlength\eqncolwid
\newcommand\eqntext[2][0pt]{%
  \setlength\parindent{0pt}%
      \setlength\eqnindent{#1}\setlength\eqncolwid{\linewidth}%
  \setlength\eqncolwid{\dimexpr\linewidth-\eqnindent}%
  \hspace*{\eqnindent}\parbox{\eqncolwid}{#2}%
}

@@

%............................................................................%
\subsubsection{Motion Model}
Our motion model (Eq.~\ref{eq:motion_model}) is a simple Gaussian transition 
centered around each particle's current position, augmented with an 
$\epsilon$-random uniform sampling strategy. In Eq.~\ref{eq:motion_model}, 
$x^{[i]}_t$ is the state of the $i^\text{th}$ particle at time $t$, $\Sigma$ 
is a chosen covariance matrix, and $b$ is vector of the height and width of 
the camera frame.
\begin{equation}
\label{eq:motion_model}
x^{[i]}_t \sim \begin{cases}
\mathcal{N}(x^{[i]}_{t-1}, \Sigma), &\text{with probability } 1-\epsilon \\
\mathcal{U}(0,b),& \text{with probability } \epsilon \\
\end{cases}\\
\end{equation}
The experiments presented in this paper used a diagonal covariance matrix 
with variance 256, and an $\epsilon$ of 0.3. We find that the Gaussian 
transition model is sufficient for tracking motion in which frame-to-frame 
position changes are relatively small. The $\epsilon$-random uniform 
transitions increase tracking robustness, by forcing the filter to always 
sample all of the pixel space. This prevents overconfidence and collapse, 
and decreases reacquisition delay.

%............................................................................%
\subsubsection{Emission Model}
Our emission model (Eq.~\ref{eq:emission_model}) effectively performs.

%----------------------------------------------------------------------------%
\subsection{Cooperative Visual Servoing}
\label{sec:visual_servoing_concept}
Remote guidance of the H$^2$Bird is performed by commanding relative changes in the
reference orientation. With estimates of the vehicle pose, we calculate an altitude
error and horizontal error. Incremental changes to the H$^2$Bird pitch and yaw are
then commanded according to a PID control law, with positive altitude error
corresponding to negative incremental pitches and positive horizontal error
corresponding to negative incremental yaw. The controller integrator term is windowed
to prevent windup when the bird is being launched, and the derivative term was tuned
by hand to dampen oscillations associated with the system latency [?].

>>>>

%----------------------------------------------------------------------------%
% PACKAGES
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\providecommand{\norm}[1]{\lVert#1\rVert}

@@

%............................................................................%
\subsubsection{Motion Model}
Our motion model (Eq.~\ref{eq:motion_model}) is a simple Gaussian transition 
centered around each particle's current position, augmented with an 
$\epsilon$-random uniform sampling strategy. In Eq.~\ref{eq:motion_model}, 
$x^{[i]}_t$ is the state of the $i^\text{th}$ particle at time $t$, $\Sigma$ 
is a chosen covariance matrix, and $b$ is vector of the height and width of 
the camera frame.
\begin{equation}
\label{eq:motion_model}
x^{[i]}_t \sim \begin{cases}
\mathcal{N}(x^{[i]}_{t-1}, \Sigma), &\text{with probability } 1-\epsilon \\
\mathcal{U}(0,b),& \text{with probability } \epsilon \\
\end{cases}\\
\end{equation}
The experiments presented in this work use a diagonal covariance matrix 
with variance 256, and an $\epsilon$ of 0.3. We find that the Gaussian 
transition model is sufficient for tracking motion in which frame-to-frame 
position changes are relatively small. The $\epsilon$-random uniform 
transitions increase tracking robustness, by forcing the filter to always 
sample all of the pixel space. This prevents overconfidence and collapse, 
and decreases reacquisition delay.

%............................................................................%
\subsubsection{Emission Model}
Our emission model (Eq.~\ref{eq:emission_model}) implements a sampling
approach to motion tracking via na\"{i}ve background subtraction[CITATION].
\begin{equation}
\label{eq:emission_model}
w^{[i]}_t = 1 + \norm{f_0(x^{[i]}_t)-f_t(x^{[i]}_t)}^2
\end{equation} 
The system provides the emission model with $f_0$, the frame representing 
the background and $f_t$, the most recent frame captured. The model assigns 
a weight $w^{[i]}_t$ to each particle $x^{[i]}_t$, proportional to the color 
distance in RGB space between the pixels of $f_0$ and $f_t$ at the location 
$x^{[i]}_t$. Hence, particles are more likely to be resampled in portions of 
the image which appear different from the background.

For the experiments presented in this work, we assumed that neither the bird 
nor any other moving object were visible in the first frame captured on system 
start. We saved the first frame captured by the system, and provided it as 
the background frame $f_0$ for every iteration of the particle filter. This 
resulted in a sampling approach to na\"{i}ve background subtraction.

Na\"{i}ve background subtraction is brittle to changes in the scene over 
time[CITATION]. However, we found it very efficient, and reliable enough for the 
short time spans necessary for H$^2$Bird to successfully negotiate narrow 
openings, which are typically less than five seconds. Substituting $f_0$ 
with a more sophisticated extraction of the background would implement a 
more sophisticated approach to background subtraction, with no changes to 
the underlying motion tracking filter.

%----------------------------------------------------------------------------%
\subsection{Cooperative Visual Servoing}
\label{sec:visual_servoing_concept}
